### 2022-03-30 manuscript/thesis.tex
ISU thesis format CC all contained in manuscript folder

\begin{document}
\SweaveOpts{concordance=TRUE}
\DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png}
%\begin{singlespace}
\def\@makechapterheada{\vspace*{-2cm}\titlepage} % in order to reduce the space between margin and heading in titlepage
\include{Preface/titlepage}
%\end{singlespace}

@@

<<eval = FALSE>>=
preddf1
#  family param1 param2 param3 weights
#1  Lnorm    2.0      1     NA     0.3
#2   Norm    2.1      1     NA     0.7

preddf2
#  family param1 param2 param3 weights
#1   Norm    1.5      1     NA     0.4
#2   Norm    4.0      2     NA     0.6

#make mixture distributions from prediction submissions
mdist1 <- MakeDist(preddf1)
mdist2 <- MakeDist(preddf2)

#make pdfs for mixture predictions
dmdist1 <- function(x) {distr::d(mdist1)(x)}
dmdist2 <- function(x) {distr::d(mdist2)(x)}

#make cdfs for mixture predictions
pmdist1 <- function(x) {distr::p(mdist1)(x)}
pmdist2 <- function(x) {distr::p(mdist2)(x)}
@

@@

<<eval=FALSE>>=
#realized observation
ob <- 3

#LogS for predictions at the realized observation
-log(dmdist1(ob)) # => 1.547238
-log(dmdist2(ob)) # => 1.848796

#CRPS for predictions at the realized observation
CRPS(pmdist1,y=ob) # => 0.6348212
CRPS(pmdist2,y=ob) # => 0.5306083
@

@@

<<eval=FALSE>>=
#posterior model probability for calculating weights
w1 <- pmdist1(ob)/(pmdist1(ob) + pmdist2(ob))
w2 <- 1-w1
#w1 => 0.5286434
#w2 => 0.4713566

#build ensemble with calculated weights
ensdist <- distr::UnivarMixingDistribution(mdist1,
                                           mdist2,
                                           mixCoeff = c(w1,w2))

#pdf and cdf for ensemble
densdist <- function(x) {(distr::d(ensdist)(x))}
pensdist <- function(x) {(distr::p(ensdist)(x))}

#LogS for predictions at the realized observation
-log(densdist(ob)) # => 1.678156

#CRPS for predictions at the realized observation
CRPS(pensdist,y=ob) # => 0.5486368
@

@@

The following is the code to make the \texttt{MakeDist()} function introduced 
in \ref{section:tools}.
<<eval=FALSE>>=
MakeDist <- function(distsdf){

  distdf <- distsdf[distsdf[,1] != 'Lst',]
  tdist <- distsdf[distsdf[,1] == 'Lst',]

  fun_dist <- 
    apply(distdf, FUN=function(x) {
      paste('distr::',x[1], '(', 
            ifelse(!is.na(x[2]) & (!is.na(x[3]) | !is.na(x[4])),
                   paste(x[2],',',sep=''),
                   ifelse(!is.na(x[2]) & is.na(x[3]) & is.na(x[4]),
                          x[2], '')), 
            ifelse(!is.na(x[3]) & !is.na(x[4]),
                   paste(x[3],',',sep=''),
                   ifelse(!is.na(x[3]) & is.na(x[4]), x[3],'')), 
            ifelse(!is.na(x[4]),x[4],''), ')',sep='')
    }, MARGIN = 1
    )

  fun_tdist <- apply(tdist, FUN=function(x) {
    paste0('distr::Td(',x[4],')*',x[3], '+', x[2])
  }, MARGIN = 1
  )

  dist_args <- paste(fun_dist, collapse=',',sep='')
  tdist_args <- paste0(fun_tdist,collapse=',')
  args <- ifelse(tdist_args!='',paste(dist_args,tdist_args,sep=','),dist_args)

  weights <- c(distdf[,5],tdist[,5])
  mixString <- paste('distr::UnivarMixingDistribution(',
                     args,',mixCoeff=weights)',sep='')
  mixDist <- eval(parse(text=mixString))

  return(mixDist)
}
@

The following is the code used to make the function \texttt{CRPS()} used in
section \ref{section:tools}.
<<eval=FALSE>>=
crps_integrand <- function(x,dist,y) {(dist(x) - as.numeric(y <= x))^2}

CRPS <- function(y,dist) {
  int <- integrate(crps_integrand,-Inf,Inf,y,dist=dist)
  return(int$value)
}
@

>>>>

\usepackage{Sweave}
\begin{document}
\input{thesis-concordance}
\DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png}
%\begin{singlespace}
\def\@makechapterheada{\vspace*{-2cm}\titlepage} % in order to reduce the space between margin and heading in titlepage
\include{Preface/titlepage}
%\end{singlespace}

@@

\begin{Schunk}
\begin{Sinput}
> preddf1
> #  family param1 param2 param3 weights
> #1  Lnorm    2.0      1     NA     0.3
> #2   Norm    2.1      1     NA     0.7
> 
> preddf2
> #  family param1 param2 param3 weights
> #1   Norm    1.5      1     NA     0.4
> #2   Norm    4.0      2     NA     0.6
> 
> 
> 
> #make mixture distributions from prediction submissions
> mdist1 <- MakeDist(preddf1)
> mdist2 <- MakeDist(preddf2)
> #make pdfs for mixture predictions
> dmdist1 <- function(x) {distr::d(mdist1)(x)}
> dmdist2 <- function(x) {distr::d(mdist2)(x)}
> #make cdfs for mixture predictions
> pmdist1 <- function(x) {distr::p(mdist1)(x)}
> pmdist2 <- function(x) {distr::p(mdist2)(x)}
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> #realized observation
> ob <- 3
> #LogS for predictions at the realized observation
> -log(dmdist1(ob)) # => 1.547238
> -log(dmdist2(ob)) # => 1.848796
> #CRPS for predictions at the realized observation
> CRPS(pmdist1,y=ob) # => 0.6348212
> CRPS(pmdist2,y=ob) # => 0.5306083
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> #posterior model probability for calculating weights
> w1 <- pmdist1(ob)/(pmdist1(ob) + pmdist2(ob))
> w2 <- 1-w1
> #w1 => 0.5286434
> #w2 => 0.4713566
> 
> #build ensemble with calculated weights
> ensdist <- distr::UnivarMixingDistribution(mdist1,
+                                            mdist2,
+                                            mixCoeff = c(w1,w2))
> #pdf and cdf for ensemble
> densdist <- function(x) {(distr::d(ensdist)(x))}
> pensdist <- function(x) {(distr::p(ensdist)(x))}
> #LogS for predictions at the realized observation
> -log(densdist(ob)) # => 1.678156
> #CRPS for predictions at the realized observation
> CRPS(pensdist,y=ob) # => 0.5486368
\end{Sinput}
\end{Schunk}

@@

The following is the code to make the \texttt{MakeDist()} function introduced 
in \ref{section:tools}.
\begin{Schunk}
\begin{Sinput}
> MakeDist <- function(distsdf){
+   
+   distdf <- distsdf[distsdf[,1] != 'Lst',]
+   tdist <- distsdf[distsdf[,1] == 'Lst',]
+   
+   fun_dist <- 
+     apply(distdf, FUN=function(x) {
+       paste('distr::',x[1], '(', 
+             ifelse(!is.na(x[2]) & (!is.na(x[3]) | !is.na(x[4])),
+                    paste(x[2],',',sep=''),
+                    ifelse(!is.na(x[2]) & is.na(x[3]) & is.na(x[4]),
+                           x[2], '')), 
+             ifelse(!is.na(x[3]) & !is.na(x[4]),
+                    paste(x[3],',',sep=''),
+                    ifelse(!is.na(x[3]) & is.na(x[4]), x[3],'')), 
+             ifelse(!is.na(x[4]),x[4],''), ')',sep='')
+     }, MARGIN = 1
+     )
+   
+   fun_tdist <- apply(tdist, FUN=function(x) {
+     paste0('distr::Td(',x[4],')*',x[3], '+', x[2])
+   }, MARGIN = 1
+   )
+   
+   dist_args <- paste(fun_dist, collapse=',',sep='')
+   tdist_args <- paste0(fun_tdist,collapse=',')
+   args <- ifelse(tdist_args!='',paste(dist_args,tdist_args,sep=','),dist_args)
+   
+   weights <- c(distdf[,5],tdist[,5])
+   mixString <- paste('distr::UnivarMixingDistribution(',
+                      args,',mixCoeff=weights)',sep='')
+   mixDist <- eval(parse(text=mixString))
+   
+   return(mixDist)
+ }
\end{Sinput}
\end{Schunk}

The following is the code used to make the function \texttt{CRPS()} used in
section \ref{section:tools}.
\begin{Schunk}
\begin{Sinput}
> crps_integrand <- function(x,dist,y) {(dist(x) - as.numeric(y <= x))^2}
> CRPS <- function(y,dist) {
+   int <- integrate(crps_integrand,-Inf,Inf,y,dist=dist)
+   return(int$value)
+ }
\end{Sinput}
\end{Schunk}
